Models of Lambek calculus with subexponentials

### 2019-06-24 PaperDraft.tex
updates in quantic conuclei proofs

\newpage

@@

  Let $c \in Q_{I_1}$. Similarly to the previous part, $c = I_1 c \leq I_2 c \leq c$, then $c \in Q_{I_2}$ and
  $I_1$ is a strong square increasing.
\end{enumerate}
\end{proof}

>>>>

@@

  Let $c \in Q_{I_1}$. Similarly to the previous part, $c = I_1 c \leq I_2 c \leq c$, then $c \in Q_{I_2}$ and
  $I_1$ is a strong square increasing:

  $\begin{array}{lll}
  &I_1 a \cdot b = \bigvee \{ q \in Q_{I_1} \: | \: q \leq a \} \cdot b = & \\
  & \:\:\:\:\:\:\:\: \text{By quantale axiom}& \\
  & \bigvee \{ q \cdot b \: | \: q \in Q_{I_1}, q \leq a \} = & \\
  & \:\:\:\:\:\:\:\: \text{As we proved above}& \\
  & \bigvee \{ I_2 q \cdot b \: | \: q \in Q_{I_1}, q \leq a \} \leq & \\
  & \:\:\:\:\:\:\:\: \text{By condition}& \\
  & \bigvee \{ I_2 q \cdot b \cdot I_2 q \: | \: q \in Q_{I_1}, q \leq a \} = & \\
  & \:\:\:\:\:\:\:\: \text{So far as $q$ is a fixpoint of $I_2$} & \\
  & \bigvee \{ q \cdot b \cdot q \: | \: q \in Q_{I_1}, q \leq a \} = & \\
  & \:\:\:\:\:\:\:\: \text{By quantale axiom} = & \\
  & \bigvee \{ q \cdot b \: | \: q \in Q_{I_1}, q \leq a \} \cdot \bigvee \{ q \in Q_{I_1} \: | \: q \leq a \} = & \\
  & \:\:\:\:\:\:\:\: \text{By quantale axiom} = & \\
  & \bigvee \{ q \in Q_{I_1} \: | \: q \leq a \} \cdot b \cdot \bigvee \{ q \in Q_{I_1} \: | \: q \leq a \} = & \\
  & \:\:\:\:\:\:\:\: \text{By Lemma } = & \\
  &I_1 a \cdot b \cdot I_1&
  \end{array}$

  The second inequation might be proved similarly.
\end{enumerate}
\end{proof}
